An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2019-01-08 algorithm_radix.Rmd
fixing toy example tasmania

@@

## Hexagon grid
Create a grid of hexagon centroids using the `create_grid` function.

@@

```{r}
grid <- grid %>%
    mutate(hex_long_int = dense_rank(hex_long)-1,
        hex_lat_int = dense_rank(hex_lat)-1)
```

There are more points than necessary on this grid.
To filter the grid for appropriate hexagons for allocation,
the `create_buffer` function is used.

```{r}
return_grid <- create_buffer(centroids, grid, hex_size, buffer_dist)
```

### Step 2: Rolling windows
The rows and columns are divided into 20 groups. The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.

@@

@@

```{r}
#map closest focal point function
```

@@

```{r}
#loop of centroid allocation
```

>>>>

tas_lga <- tas_lga %>%
    sf::st_transform(., crs = projstring)

@@

```{r, fig.cap="Tasmanian Local Government Areas and derived centroids."}
fort_tas <- fortify_sfc(tas_lga, projstring = projstring)
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude),data= centroids)
```

## Hexagon grid

Create a grid of hexagon centroids using the `create_grid` function.

@@

```{r}
full_grid <- grid %>%
    mutate(hex_long_int = dense_rank(hex_long)-1,
        hex_lat_int = dense_rank(hex_lat)-1)
```

There are more points than necessary on this grid.

### Step 2: Rolling windows

To filter the grid for appropriate hexagons for allocation,
the `create_buffer` function is used.

```{r}
grid <- create_buffer(centroids, full_grid, hex_size, buffer_dist)
```

The rows and columns are divided into 20 groups. The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.

@@

```{r}
ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "black", data = full_grid, size = 0.5) +
  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = grid, size = 0.75)
```

@@

```{r}
# Split the centroid data set
centroids <- centroids %>% 
  nest(longitude, latitude) %>% 
  mutate(closest = map(data, closest_focal_point, focal_points = focal_points)) %>% 
  unnest(data, closest) %>% 
  arrange(focal_distance)
```

@@

Define a distance around a centroid to consider for possible hexagon location.

```{r}
## Not necessary within `create_hexmap`:
## Consider hexagon points up to a certain distance from centroid

filter_dist <- (hex_size)*10
```

Allocate each centroid, beginning with the closest to a focal point, extending to the furthest. Will preserve spatial relationship.

```{r}
hexmap_allocation <- allocate(centroids = centroids,
        hex_grid = grid,
        hex_size = hex_size,
        filter_dist = filter_dist,
        width = width,
        focal_points = focal_points,
        verbose = TRUE,
        id = sf_id)
```
